\section{Evaluation}
\label{sec:evaluation}

We present three Verilator~\cite{verilator}-based simulations on a $4\times4$
HyNoC mesh, each targeting a different evaluation goal:
\begin{enumerate}
  \item \textbf{Latency characterization.}  A lightweight GeMV
        (General Matrix-Vector multiplication, $\mathbf{y}=A\mathbf{x}$) with a
        $16\times4$ matrix produces clean per-hop measurements that establish
        the deterministic per-hop latency discussed in
        Section~\ref{sec:switching}.
  \item \textbf{LLaMA~3~8B FFN benchmark (single master).}  A full-scale
        GeMV at LLaMA~3~8B FFN up-projection dimensions
        ($14336\times4096$) with Q8\_0 weights and BF16 activations
        demonstrates the network under realistic AI inference workload.
  \item \textbf{Four-master throughput scaling.}  The same LLaMA~3~8B-scale
        benchmark is replicated across four corner masters, each owning a
        $2\times2$ quadrant, to quantify the speedup from distributed
        injection.
\end{enumerate}
All three benchmarks share the same 16-router $4\times4$ mesh and cover the
full communication cycle: data scatter from the master(s), computation at
worker nodes, and result gather.

\subsection{Experimental Setup}

\textbf{Network Topology.}

The network consists of 16~\texttt{hynoc\_router\_5p} instances arranged as
a $4\times4$ 2D mesh, as shown in Figure~\ref{fig:mesh4x4}.  Routers are
addressed by $(r,c)$ with $r\in\{0,1,2,3\}$ (row, top-to-bottom) and
$c\in\{0,1,2,3\}$ (column, left-to-right).  Port convention per router:
0\,=\,Local, 1\,=\,East, 2\,=\,South, 3\,=\,West, 4\,=\,North.  Each
router's local port (port~0) attaches a processing node; neighboring routers are
cross-linked on their directional ports (e.g., router $(r,c)$ port~1 connects to
router $(r,c{+}1)$ port~3).

\begin{figure}[t]
  \centering
  \begin{tikzpicture}[
    rtr/.style={circle, draw, font=\scriptsize, inner sep=1pt, minimum size=22pt},
    mst/.style={circle, draw, fill=black!18, font=\scriptsize\bfseries, inner sep=1pt,
                minimum size=22pt},
    >=stealth,
    route/.style={->, line width=1.6pt, color=black!55}
  ]
  \def\S{1.6}
  % Horizontal links
  \foreach \row in {0,...,3}{
    \foreach \col in {0,...,2}{
      \draw[<->] ({\col*\S+0.16},{-\row*\S}) -- ({\col*\S+\S-0.16},{-\row*\S});
    }
  }
  % Vertical links
  \foreach \row in {0,...,2}{
    \foreach \col in {0,...,3}{
      \draw[<->] ({\col*\S},{-\row*\S-0.16}) -- ({\col*\S},{-\row*\S-\S+0.16});
    }
  }
  % All nodes
  \foreach \row in {0,...,3}{
    \foreach \col in {0,...,3}{
      \node[rtr] at ({\col*\S},{-\row*\S}) {\row,\col};
    }
  }
  % Master override
  \node[mst] at (0,0) {\textbf{M}};
  % Sample route (0,0)→(2,3): East×3, South×2
  \draw[route] (0,0) -- ({\S},0) -- ({2*\S},0) -- ({3*\S},0)
               -- ({3*\S},{-\S}) -- ({3*\S},{-2*\S});
  \end{tikzpicture}
  \caption{$4\times4$ mesh topology. \textbf{M} = master at $(0,0)$; remaining
           nodes are workers at $(r,c)$.  Bidirectional links are full-duplex
           (independent ingress and egress).  The gray arrow illustrates the XY
           route from the master to worker $(2,3)$: three East hops followed by two
           South hops, then a final local hop ($H=6$).}
  \label{fig:mesh4x4}
\end{figure}

The master node resides at $(0,0)$.  It sequentially distributes data to all 15
worker nodes and collects their results.

\subsection{Experiment 1: Latency Characterization}

\subsubsection{Computation and Communication Model}

The benchmark computes $\mathbf{y} = A\mathbf{x}$ with $A\in\mathbb{R}^{16\times4}$
and $\mathbf{x}=[1,2,3,4]^T$.  Worker $(r,c)$ is responsible for one scalar inner
product: $y_{4r+c} = \langle A_{4r+c},\, \mathbf{x} \rangle$.

\textbf{Forward packet} (master to worker $(r,c)$): one routing flit, one tag
flit, four flits for the matrix row $A_{4r+c}$, and four flits for
$\mathbf{x}$, totaling ten flits.  After the routing flit is consumed by the
network, the worker receives $P_\text{fwd}=9$ payload flits.

\textbf{Return packet} (worker to master): one routing flit, one tag flit, and one
result flit.  The master receives $P_\text{ret}=2$ payload flits.

Workers compute the inner product instantaneously, so the total simulation time
is dominated by communication latency and the sequential injection schedule at
the master.

\textbf{Route construction.}  Hop lists are built following dimension-order
(XY) order: East/West moves bring the packet to the target column, North/South
moves bring it to the target row, and a final local hop delivers it.  This
eliminates cyclic channel dependencies and guarantees deadlock
freedom~\cite{dally1987}.  All packets use standard unicast source routing
(proto \texttt{4'b0000}); the dedicated XY proto field (\texttt{4'b1000})
reserved in Table~\ref{tab:proto} is not exercised in these experiments.
A route from $(r_0,c_0)$ to $(r_1,c_1)$ requires
\begin{equation}
  H = |c_1-c_0| + |r_1-r_0| + 1
  \label{eq:hops-xy}
\end{equation}
hops, where the $+1$ accounts for the final local hop at the destination.
Throughout this section $H$ always counts all hops including that local hop.
For the master at $(0,0)$, this simplifies to $H=r+c+1$.  Routes are encoded as source-routing flits using the relative hop
encoding described in Section~\ref{sec:architecture}.

\textbf{Simulation Infrastructure.}

The Verilator C++ model instantiates 16~\texttt{Vhynoc\_router\_5p} objects
sharing one \texttt{VerilatedContext}.  Inter-router links are modeled as
one-cycle latches: egress signals are captured after each rising clock edge and
applied to the neighbor's ingress before the next rising edge.  This one-cycle
propagation delay is physically accurate for a registered synchronous
interconnect.

Each router drives a single clock (\texttt{router\_clk} and all
\texttt{portX\_ingress\_clk} toggled together).  In dual-clock mode
(\texttt{SINGLE\_CLOCK\_ROUTER=0}), the ingress dual-clock FIFOs internally
use gray-code CDC synchronization even when source and destination clocks are
the same signal; in single-clock mode (\texttt{SINGLE\_CLOCK\_ROUTER=1}), the
gray-code pipeline is bypassed.

\subsubsection{Latency Results}

Table~\ref{tab:latency} reports the \emph{return-path} latency for each hop
count $H$ in both configurations.  Return-path measurements are free of
source-queuing effects (each worker sends exactly one result as soon as
computation completes), yielding clean linear fits.

\begin{table}[h]
\centering
\footnotesize
\setlength{\tabcolsep}{4pt}
\caption{Measured return-path latency ($P=2$, cycles) vs.\ hop count.
         Dual = dual-clock FIFO (\texttt{SINGLE\_CLOCK\_ROUTER=0});
         Single = single-clock FIFO (\texttt{SINGLE\_CLOCK\_ROUTER=1});
         $\Delta$ = Dual$-$Single.}
\label{tab:latency}
\begin{tabular}{@{}rrrr@{}}
\toprule
$H$ & Dual & Single & $\Delta$ \\
\midrule
2 & 25 & 19 &  6 \\
3 & 37 & 28 &  9 \\
4 & 49 & 37 & 12 \\
5 & 61 & 46 & 15 \\
6 & 73 & 55 & 18 \\
7 & 85 & 64 & 21 \\
\bottomrule
\end{tabular}
\end{table}

The measured return-path latencies satisfy exact linear fits:
\begin{align}
  L_\text{dual}   &= 12H + P - 1 \label{eq:lfit-dual}   \\
  L_\text{single} &= 9H + P - 1  \label{eq:lfit-single}
\end{align}
matching the linear, deterministic form of~(\ref{eq:latency}) with a fixed
per-hop cost of $\alpha=12$ cycles in dual-clock mode and $\alpha=9$ in
single-clock mode, and no load-dependent term.  This per-hop cost is the
pipeline traversed at each router---ingress FIFO read, routing-FSM request
register, PRRA grant, and egress data register---together with the one-cycle
registered inter-router link of the co-simulation harness.  The
$3$-cycle-per-hop difference between the two modes ($\alpha=12$ versus $9$) is
exactly the depth of the dual-clock FIFO's gray-code
synchroniser~\cite{cummings2002}, which the single-clock FIFO does not
instantiate.  This difference is constant across all hop counts, so the latency
stays perfectly linear and predictable in both modes.

The total simulation time is \textbf{391~cycles} in dual-clock mode and
\textbf{349~cycles} in single-clock mode ($-$10.7\%).  All 16 computed
results are correct in both runs.

\subsubsection{Link Utilization}

Table~\ref{tab:links} summarizes link utilization over the 391-cycle dual-clock run.
Traffic is inherently asymmetric: the master sends all forward packets via its East
port first, concentrating load on the East-bound links of row~0.

\begin{table}[h]
\centering
\footnotesize
\setlength{\tabcolsep}{4pt}
\caption{Link utilization (\%) by directed link (dual-clock, 391~cycles).
         Each row names one router-to-router link.
         Links with $<$0.5\% utilization omitted; overall average: 3.3\%.}
\label{tab:links}
\begin{tabular}{@{}llr@{}}
\toprule
Direction & Link & Util\,(\%) \\
\midrule
\multirow{3}{*}{$\to$East, row\,0}
  & $(0,0)\!\to\!(0,1)$ & 30.7 \\
  & $(0,1)\!\to\!(0,2)$ & 20.5 \\
  & $(0,2)\!\to\!(0,3)$ & 10.2 \\
\cmidrule(l){1-3}
\multirow{3}{*}{$\to$South, col\,0}
  & $(0,0)\!\to\!(1,0)$ &  7.7 \\
  & $(1,0)\!\to\!(2,0)$ &  5.1 \\
  & $(2,0)\!\to\!(3,0)$ &  2.6 \\
\cmidrule(l){1-3}
$\to$North, col\,0
  & $(1,0)\!\to\!(0,0)$ &  9.2 \\
\cmidrule(l){1-3}
\multirow{3}{*}{$\to$West, row\,0}
  & $(0,1)\!\to\!(0,0)$ &  2.3 \\
  & $(0,2)\!\to\!(0,1)$ &  1.5 \\
  & $(0,3)\!\to\!(0,2)$ &  0.8 \\
\bottomrule
\end{tabular}
\end{table}

East-bound utilization halves at each column of row~0, consistent with XY
routing: each router delivers one packet to its local worker and forwards the
rest eastward.  The overall average of 3.3\% reflects the sequential master
bottleneck: with a single sender issuing one packet at a time, most links are
idle.

\subsection{Experiment 2: LLaMA~3~8B FFN Benchmark}

\subsubsection{Single-Master Configuration}
\label{sec:large-matmul}

To assess HyNoC under a realistic AI inference workload we scale the benchmark
to the LLaMA~3~8B~\cite{llama3} FFN up-projection layer.  In transformer
models, the Feed-Forward Network (FFN) consists of two linear projections with
a nonlinearity in between; the \emph{up-projection} is the first of these,
expanding the representation from the model dimension $D_\text{in}=4096$ to
the intermediate dimension $D_\text{out}=14336$.  The benchmark computes
$\mathbf{y}=W\mathbf{x}$ with $W\in\mathbb{R}^{14336\times4096}$ and
$\mathbf{x}\in\mathbb{R}^{4096}$.

Weights are stored in the Q8\_0 quantization format used by
llama.cpp~\cite{llama_cpp}: each weight is an 8-bit signed integer, and one
FP16 (16-bit floating-point) scale factor is shared per block of 32 weights to
recover approximate FP32 values at decode time.  Mapping to flits: the FP16
scale occupies the lower 16~bits of one 32-bit flit (upper 16~bits zero), and
the 32 int8 weights are packed four per flit, requiring 8~flits --- hence
9~flits per Q8\_0 block.  Activations use the BF16 format (Brain
Float~16: 1~sign bit, 8~exponent bits, 7~mantissa bits), packed two values per
32-bit flit.  Results are accumulated and returned in FP32 (IEEE~754 single
precision).

\textbf{Forward packet} (master to worker, for one output row): one routing
flit, one tag flit, 128~Q8\_0 blocks~$\times$~(1~scale flit + 8~weight flits),
and 2048~BF16 activation flits, totaling $P_\text{fwd}=3201$ payload flits.

\textbf{Return packet}: one routing flit, one tag flit, and one FP32 result
flit --- $P_\text{ret}=2$ payload flits, identical to the latency experiment.

\textbf{Computation model.}  Each of the 15~worker nodes is assigned
$14336/16 = 896$ output rows; the master at $(0,0)$ also computes 896~rows
locally.  Workers decode Q8\_0 weights to FP32 and accumulate the dot product
in FP32.  Local computation is modeled as instantaneous: injecting one forward
packet takes 3202~clock cycles (one per flit), which already exceeds the
dot-product budget of a real VLIW unit over 4096~elements, so arithmetic
is not the bottleneck.  All
14\,336~results are verified for exact FP32 equality against a software
reference.

\textbf{Throughput.}  The simulation completes in \textbf{43\,102\,246~cycles}
(dual-clock FIFO, \texttt{SINGLE\_CLOCK\_ROUTER=0})
with the master's single egress port sustaining near-100\% injection throughout.
Link utilization (Table~\ref{tab:links-llama}) shows the consequence of this
sustained injection: link $(0,0)\!\to\!(0,1)$ reaches 79.9\%,
carrying packets bound for all 12~workers that need at least one East hop.
Utilization falls in proportion to the number of remaining destinations on
each successive link.  South-bound links absorb $\tfrac{1}{4}$ of the total
traffic each.  Return-path links (West and North) are negligible at $<$0.1\%.
The overall average of \textbf{6.7\%} reflects the single-port injection
bottleneck: 47~of 48~directed links are underutilised while one port
saturates.  Repeating the run in single-clock mode
(\texttt{SINGLE\_CLOCK\_ROUTER=1}) yields \textbf{43\,102\,204~cycles}, only
42~cycles below the dual-clock result.  This confirms that the workload is
\emph{injection-bound} rather than latency-bound: runtime is dominated by the
one-flit-per-cycle injection of the 3201-flit forward packets, so the per-hop
latency saved by single-clock operation---the $9H$ versus $12H$ slope
of~(\ref{eq:lfit-single}) and~(\ref{eq:lfit-dual})---is negligible against the
tens of millions of injection cycles.  The four-master run is likewise
unchanged (8\,620\,466~cycles single-clock versus 8\,620\,484 dual-clock), so
the $5\times$ speedup is mode-independent.  Single-clock operation benefits
only latency-dominated traffic, such as the Experiment~1 latency test, where it
reduced the total from 391 to 349~cycles.

\begin{table}[h]
\centering
\footnotesize
\setlength{\tabcolsep}{4pt}
\caption{Link utilization (\%) by directed link, LLaMA~3~8B single-master run
         (43\,102\,246~cycles).  All four South columns are symmetric.
         Return-path links ($<$0.1\%) omitted; overall average: 6.7\%.}
\label{tab:links-llama}
\begin{tabular}{@{}llr@{}}
\toprule
Direction & Link & Util\,(\%) \\
\midrule
\multirow{3}{*}{$\to$East, row\,0}
  & $(0,0)\!\to\!(0,1)$ & 79.9 \\
  & $(0,1)\!\to\!(0,2)$ & 53.2 \\
  & $(0,2)\!\to\!(0,3)$ & 26.6 \\
\cmidrule(l){1-3}
\multirow{3}{*}{$\to$South, all cols}
  & $(0,k)\!\to\!(1,k)$, $k=0\text{--}3$ & 20.0 \\
  & $(1,k)\!\to\!(2,k)$, $k=0\text{--}3$ & 13.3 \\
  & $(2,k)\!\to\!(3,k)$, $k=0\text{--}3$ &  6.7 \\
\bottomrule
\end{tabular}
\end{table}

The load on each segment is strictly proportional to the number of destinations
reachable through it (East: 12, 8, 4 workers; South per column: 3, 2, 1
workers), with no hot-spots beyond the first East segment.  Nonetheless, the
bottleneck remains the single injection port, motivating the multi-master
extension.

\subsubsection{Four-Master Quadrant Configuration}
\label{sec:4master}

The single master at $(0,0)$ creates an injection bottleneck: all 15 forward
packets per round enter through one port, and all result packets return to
that same port.  We now distribute injection across the four corner nodes by
assigning each a $2\times2$ quadrant.

Table~\ref{tab:quadrants} lists the assignment.  Master~$m$ handles
$Q = D_\text{out}/4 = 3584$ output rows.  With $N_W=3$ workers per quadrant
and one row computed locally, each master executes
$\mathrm{ROUNDS}=Q/(N_W+1)=896$ \emph{rounds}---where one round consists of
sending one forward packet to each of the $N_W$ workers and computing one row
locally, then collecting $N_W$ result packets---the same count as the
single-master case, but all four masters proceed simultaneously.

\begin{table}[h]
\centering
\footnotesize
\caption{Quadrant assignment: masters, workers, and row ranges.}
\label{tab:quadrants}
\begin{tabular}{@{}clll@{}}
\toprule
Master & Position & Workers & Rows \\
\midrule
$M_0$ & $(0,0)$ & $(0,1),(1,0),(1,1)$ & $0$--$3583$ \\
$M_1$ & $(0,3)$ & $(0,2),(1,3),(1,2)$ & $3584$--$7167$ \\
$M_2$ & $(3,0)$ & $(3,1),(2,0),(2,1)$ & $7168$--$10751$ \\
$M_3$ & $(3,3)$ & $(3,2),(2,3),(2,2)$ & $10752$--$14335$ \\
\bottomrule
\end{tabular}
\end{table}

The structural property exploited here is \emph{link disjointness}: every XY
route from a corner master to its three workers stays within the $2\times2$
quadrant.  No packet crosses the horizontal midline (between rows~1 and~2) or
the vertical midline (between columns~1 and~2), so the four quadrants are
traffic-isolated by construction, without any runtime coordination.

Figure~\ref{fig:mesh4x4-4m} illustrates the topology and the three routes
from $M_0$: one East hop to $(0,1)$, one South hop to $(1,0)$, and
East+South to $(1,1)$.

\begin{figure}[t]
  \centering
  \begin{tikzpicture}[
    rtr/.style={circle, draw, font=\scriptsize, inner sep=1pt, minimum size=22pt},
    mst/.style={circle, draw, fill=black!18, font=\scriptsize\bfseries, inner sep=1pt,
                minimum size=22pt},
    >=stealth,
    route/.style={->, line width=1.4pt, color=black!65}
  ]
  \def\S{1.6}
  % Horizontal links
  \foreach \row in {0,...,3}{
    \foreach \col in {0,...,2}{
      \draw[<->] ({\col*\S+0.16},{-\row*\S}) -- ({\col*\S+\S-0.16},{-\row*\S});
    }
  }
  % Vertical links
  \foreach \row in {0,...,2}{
    \foreach \col in {0,...,3}{
      \draw[<->] ({\col*\S},{-\row*\S-0.16}) -- ({\col*\S},{-\row*\S-\S+0.16});
    }
  }
  % Quadrant boundary (dashed)
  \draw[dashed, black!40, thick]
    ({1.5*\S},{0.35}) -- ({1.5*\S},{-3.5*\S});
  \draw[dashed, black!40, thick]
    ({-0.35},{-1.5*\S}) -- ({3.5*\S},{-1.5*\S});
  % All nodes
  \foreach \row in {0,...,3}{
    \foreach \col in {0,...,3}{
      \node[rtr] at ({\col*\S},{-\row*\S}) {\row,\col};
    }
  }
  % Corner masters
  \node[mst] at (0,0)              {\textbf{M0}};
  \node[mst] at ({3*\S},0)        {\textbf{M1}};
  \node[mst] at (0,{-3*\S})       {\textbf{M2}};
  \node[mst] at ({3*\S},{-3*\S})  {\textbf{M3}};
  % Routes from M0 to its three workers
  \draw[route] (0.16,0) -- ({\S-0.16},0);
  \draw[route] (0,-0.16) -- (0,{-\S+0.16});
  \draw[route] (0.16,0) -- ({\S},0) -- ({\S},{-\S+0.16});
  \end{tikzpicture}
  \caption{Four-master $4\times4$ mesh.  Corner nodes $M_0$--$M_3$ (shaded)
           each coordinate a $2\times2$ quadrant; dashed lines mark the mesh
           midpoints.  Arrows show $M_0$'s three routes to workers $(0,1)$,
           $(1,0)$, and $(1,1)$.  By symmetry, routes from all four masters
           remain within their respective quadrant.}
  \label{fig:mesh4x4-4m}
\end{figure}

\emph{Computation model.}  Each master computes one row locally per round
(row $mQ + t(N_W+1)$ in round~$t$, for $t = 0,\ldots,895$), for a total
of 896 local rows per master and 3584 across all four.  Local dot products
are modeled as instantaneous: a VLIW unit over $D_\text{in}=4096$ elements
completes well within the $3\times3202$ clock-cycle injection window per round,
so arithmetic is not on the critical path.  All 14\,336 results are verified
for exact FP32 equality against a software reference.

\subsubsection{Throughput Scaling Results}

The four-master simulation completes in \textbf{8\,620\,484~cycles}, a
$\mathbf{5.0\times}$ speedup over the 43\,102\,246~cycles of the
single-master run (Table~\ref{tab:throughput}).

\begin{table}[h]
\centering
\footnotesize
\setlength{\tabcolsep}{4pt}
\caption{Single- vs.\ four-master throughput
         ($D_\text{out}=14336$, $P_\text{fwd}=3201$ payload flits).}
\label{tab:throughput}
\begin{tabular}{@{}lrrr@{}}
\toprule
Configuration & Masters & Cycles & Speedup \\
\midrule
Single master & 1 & 43\,102\,246 & $1\times$ \\
Four masters  & 4 &  8\,620\,484 & $5\times$ \\
\bottomrule
\end{tabular}
\end{table}

The $5\times$ gain exceeds the $4\times$ expected from simple injection
parallelism.  The additional margin comes from backpressure relief: each
corner master serves only three workers, whereas the single master drives
fifteen.  With fewer concurrent result packets converging on one egress
port, injection stalls are shorter.

Table~\ref{tab:links4m} reports the utilization pattern.  The quadrant
isolation property is confirmed quantitatively: every link crossing either
mesh midpoint registers exactly 0\%.  This zero-overhead isolation is a
direct consequence of source routing: routes are computed statically and
encoded entirely in the packet header, so no router-internal mechanism is
needed to enforce quadrant boundaries at runtime.  Within each quadrant, the first East
or West hop from the corner master reaches 66.6\% because two of the three
forward routes share it (the direct worker and the diagonal worker); each
South or North second-hop segment carries one route at 33.3\%.  By symmetry
all four quadrants show identical figures.  The overall average of 11.1\%
contrasts with the 3.3\% of the single-master run, reflecting simultaneous
injection from four ports and correspondingly more uniform mesh loading.

\begin{table}[h]
\centering
\footnotesize
\setlength{\tabcolsep}{4pt}
\caption{Representative link utilization (\%), four-master run
         (8\,620\,484~cycles).  By symmetry all four quadrants are
         identical; cross-boundary links are exactly 0\%.}
\label{tab:links4m}
\begin{tabular}{@{}llr@{}}
\toprule
Direction & Link & Util\,(\%) \\
\midrule
$\to$East, row\,0  & $(0,0)\!\to\!(0,1)$ & 66.6 \\
$\to$West, row\,0  & $(0,3)\!\to\!(0,2)$ & 66.6 \\
$\to$East, row\,3  & $(3,0)\!\to\!(3,1)$ & 66.6 \\
$\to$West, row\,3  & $(3,3)\!\to\!(3,2)$ & 66.6 \\
$\to$South, col\,0 & $(0,0)\!\to\!(1,0)$ & 33.3 \\
$\to$South, col\,1 & $(0,1)\!\to\!(1,1)$ & 33.3 \\
$\to$North, col\,0 & $(3,0)\!\to\!(2,0)$ & 33.3 \\
$\to$North, col\,1 & $(3,1)\!\to\!(2,1)$ & 33.3 \\
Cross-boundary     & (any)               &  0.0 \\
\midrule
\multicolumn{2}{@{}l}{\textbf{Overall average}} & \textbf{11.1} \\
\bottomrule
\end{tabular}
\end{table}

All results in this section are obtained from Verilator co-simulation; on-device
measurement on physical FPGA hardware remains open and is identified as future
work in Section~\ref{sec:conclusion}.
