\section{Implementation}
\label{sec:implementation}

\subsection{Repository Organization}

HyNoC is part of a larger open-source IP library hosted at
\url{https://github.com/cclienti/verilog-ip}. The repository is organized into
two complementary layers under the \texttt{hw/} directory:

\begin{itemize}
  \item \texttt{hw/lib/}: a collection of reusable, standalone Verilog IP cores
        covering arithmetic, memories, FIFOs, and arbiters. Each module ships
        with its own parameterized RTL and self-checking testbench.
  \item \texttt{hw/network/hynoc/}: the HyNoC subsystem, which builds on top of
        \texttt{hw/lib/} and is described in detail in this paper.
\end{itemize}

HyNoC directly instantiates three library modules:
\texttt{dclkfifolut} (dual-clock FIFO mapped to distributed LUT RAM, used in
\texttt{hynoc\_ingress} and \texttt{hynoc\_local\_interface}),
\texttt{sclkfifolut} (single-clock variant, used in single-clock mode), and
\texttt{prra} together with its \texttt{prra\_lut} sub-module (the parallel
round-robin arbiter, used in \texttt{hynoc\_egress}).
These components are independently verified and reusable outside HyNoC.
Relying on shared library primitives rather than vendor-specific FIFO or
arbitration IP is what makes the design portable across FPGA families.

\subsection{RTL Organization}

The HyNoC RTL is written in Verilog and organized as follows:

\begin{itemize}
  \item \texttt{hynoc\_ingress}: ingress port (dual-clock FIFO via
        \texttt{dclkfifolut}/\texttt{sclkfifolut}, routing FSM, unicast and
        multicast protocol decoder);
  \item \texttt{hynoc\_egress}: egress port (data multiplexer, PRRA via
        \texttt{prra}/\texttt{prra\_lut});
  \item \texttt{hynoc\_router\_base}: parameterized router base (crossbar wiring,
        port instantiation);
  \item \texttt{hynoc\_router\_3p} / \texttt{hynoc\_router\_5p}: 3-port and
        5-port router instances with self-checking testbenches;
  \item \texttt{hynoc\_local\_interface}: local interface for node attachment
        (output FIFO via \texttt{dclkfifolut}/\texttt{sclkfifolut});
  \item \texttt{hynoc\_stream\_reader} / \texttt{hynoc\_stream\_writer}:
        simulation traffic generators used in testbenches to inject and
        check random packet streams.
\end{itemize}

The design is parameterized by: payload width (\texttt{PAYLOAD\_WIDTH}), FIFO
depth (\texttt{LOG2\_FIFO\_DEPTH}: 2 to 64 entries), number of ports
(\texttt{NB\_PORTS}: 3 to 9), index width (\texttt{INDEX\_WIDTH}), optional
multicast routing (\texttt{ENABLE\_MCAST\_ROUTING}), and single-clock mode
(\texttt{SINGLE\_CLOCK\_ROUTER}).

\subsection{Simulation and Verification}

Each module is delivered with a self-checking testbench. The 3-port router
testbench exercises both unicast and multicast scenarios over a 2-router, 4-node
topology. The 5-port router testbenches cover five distinct traffic scenarios,
including simultaneous multi-path transfers that verify the PRRA's starvation-free
behavior.

Simulation is supported under Icarus Verilog and ModelSim. Verilator is
integrated in the build infrastructure both for linting (\texttt{--lint-only})
and for C++ co-simulation: a multi-instance Verilator model is used in
Section~\ref{sec:evaluation} to characterize end-to-end latency and link
utilization on a $4\times4$ mesh.  Waveform inspection is
automated using Wavedisp~\cite{wavedisp}, a Python module that generates
simulator-specific signal configuration scripts from a single source description,
targeting GTKWave, ModelSim, and Riviera-PRO.

\subsection{FPGA Target}

Table~\ref{tab:synth-k7} reports post-place-and-route results on two Xilinx
7-series devices: a Kintex-7 (xc7k160t-fbg484, speed grade~$-2$) targeting
370\,MHz and a Zynq-7020 (xc7z020clg484, speed grade~$-1$) targeting 200\,MHz.
Both runs use 32-bit payload and 32-entry single-clock FIFOs
(\texttt{sclkfifolut}).  \textbf{WNS} (Worst Negative Slack) is the tightest
setup slack across all register-to-register timing paths; a positive value
means the target is met, and $f_\text{max} = 1\,/\,(T_\text{clk} - \text{WNS})$.

\begin{table}[h]
\centering
\footnotesize
\setlength{\tabcolsep}{2pt}
\caption{P\&R results on two Xilinx 7-series devices (32-bit,
         32-entry \texttt{sclkfifolut}; 24\,LUT-RAM/port for ingress FIFOs).
         WNS in ns; $f_\text{max}$ in MHz.}
\label{tab:synth-k7}
\begin{tabular}{@{}l rr r rr rr@{}}
\toprule
& & & &
  \multicolumn{2}{c}{\shortstack{Kintex-7\;$-2$\\(370\,MHz)}} &
  \multicolumn{2}{c}{\shortstack{Zynq-7020\;$-1$\\(200\,MHz)}} \\
\cmidrule(lr){5-6}\cmidrule(lr){7-8}
Router & LUT & LUT & FFs & WNS & $f_\text{max}$ & WNS & $f_\text{max}$ \\
       & (log.) & (RAM) & & (ns) & (MHz) & (ns) & (MHz) \\
\midrule
3-port &  253 &  72 &  327 & $+$0.079 & 381 & $+$0.034 & 201 \\
5-port &  596 & 120 &  590 & $+$0.127 & 389 & $+$0.101 & 204 \\
7-port & 1259 & 168 &  889 & $+$0.070 & 380 & $+$0.032 & 201 \\
9-port & 1806 & 216 & 1215 & $+$0.003 & 371 & $+$0.034 & 201 \\
\bottomrule
\end{tabular}
\end{table}

LUT-RAM usage is exactly 24 per port in every configuration, reflecting the
fixed-depth FIFO at each ingress; no block RAM is consumed.  LUT counts are
device-independent to within 1\% (synthesis tool variation).  Logic LUTs grow
superlinearly with port count, driven by the PRRA whose table size scales as
$2^{N-1}$ per egress port.  FFs grow nearly linearly (109 to 135 per port),
consistent with the per-port register cost of the ingress FSM and FIFO control.
All four port counts meet their respective frequency targets on both devices,
with the 5-port configuration consistently achieving the best timing margin.

The design has been validated on both Intel (Altera) and AMD (Xilinx) FPGA
families; reference board support is included for the DE0-Nano (Cyclone~IV)
and the ZedBoard (Zynq-7000).  Both \texttt{dclkfifolut} (dual-clock) and
\texttt{sclkfifolut} (single-clock) map exclusively to distributed LUT RAM,
avoiding dependency on vendor-specific FIFO IP and ensuring portability across
FPGA families.

The AXI-Stream-compatible port interface (see Section~\ref{sec:architecture})
simplifies integration with standard FPGA IP cores. On Zynq devices for instance,
the HyNoC local interface connects directly to the Processing System AXI-Stream
DMA engine with only a thin adapter to bridge the \texttt{fifo\_level} sideband.
This reduces integration effort and allows reuse of existing AXI-Stream
verification infrastructure.

\subsection{RTL Elaboration with Veriparse}

HyNoC makes use of advanced Verilog constructs — in particular, \texttt{initial}
blocks containing \texttt{for} loops and integer arithmetic — to pre-compute the
PRRA lookup tables at elaboration time. While this is perfectly legal Verilog, some
FPGA toolchains have limited support for such constructs in synthesizable RTL.

Veriparse~\cite{veriparse} is a companion source-to-source transformation toolkit
that addresses this issue. Its \texttt{veriflat} tool performs a sequence of
elaboration-time passes on the full module hierarchy: \emph{parameter and
localparam inlining} substitutes all parameter values at instantiation sites;
\emph{constant folding} and \emph{expression evaluation} reduce symbolic
expressions to integer literals; \emph{loop unrolling} expands \texttt{for},
\texttt{while}, and \texttt{repeat} constructs; \emph{generate-block elaboration}
resolves \texttt{generate}/\texttt{endgenerate} sections; \emph{variable folding}
evaluates \texttt{initial} blocks whose control flow is entirely determined by
inlined constants; and \emph{dead-code elimination} prunes branches that can never
be taken after constant propagation. The \emph{module flattener} then inlines the
full instantiation hierarchy into a single, parameter-free module. The resulting
RTL contains only plain assignments, registers, and combinational logic, with no
remaining parametric expressions — portable across any standard Verilog toolchain.

Figure~\ref{fig:veriflat-router} illustrates parameter inlining and constant
folding on the module boundary: the parameterized \texttt{hynoc\_router\_5p}
declaration, whose port widths are symbolic expressions of \texttt{PAYLOAD\_WIDTH}
and \texttt{LOG2\_FIFO\_DEPTH}, becomes a flat declaration with all widths
resolved to integer literals. The 5-port, 32-bit configuration yields
\texttt{[32:0]} data buses and \texttt{[5:0]} FIFO level signals in the output.

\begin{figure}[t]
\textbf{Before (parameterized):}
\begin{lstlisting}
module hynoc_router_5p
  #(parameter PAYLOAD_WIDTH   = 32,
    parameter LOG2_FIFO_DEPTH = 5, ...)
   (...
    input  wire [PAYLOAD_WIDTH:0]   port0_ingress_data,
    output wire [LOG2_FIFO_DEPTH:0] port0_ingress_fifo_level,
    ...);
\end{lstlisting}
\textbf{After \texttt{veriflat} (parameters inlined):}
\begin{lstlisting}
module hynoc_router_5p
   (...
    input  wire [32:0] port0_ingress_data,
    output wire [5:0]  port0_ingress_fifo_level,
    ...);
\end{lstlisting}
\caption{\texttt{veriflat} resolves parameterized port widths into constants.}
\label{fig:veriflat-router}
\end{figure}

Figure~\ref{fig:veriflat-prra} shows a complementary transformation class
supported by \texttt{veriflat}: variable folding combined with loop unrolling.
The \texttt{initial} block of \texttt{prra\_lut} — which computes the
round-robin priority table through nested \texttt{for} loops and modular
arithmetic over inlined constants — is fully evaluated at elaboration time;
the resulting \texttt{initial} block contains only explicit constant assignments.

\begin{figure}[t]
\textbf{Before (algorithmic \texttt{initial} block):}
\begin{lstlisting}
initial begin
  lut[0] = STATE_OFFSET[LOG2_WIDTH-1:0];
  for (j=1; j<lut_length; j=j+1) begin
    lut_index = j[WIDTH-1:0];
    value = -1;
    for (k=0; k<WIDTH; k=k+1) begin
      l = (k + STATE_OFFSET + 1) % WIDTH;
      if (lut_index[l] == 1'b1)
        if (value == -1) value = l;
    end
    lut[j] = value[LOG2_WIDTH-1:0];
  end
end
\end{lstlisting}
\textbf{After \texttt{veriflat} (pre-computed, \texttt{STATE\_OFFSET=0}):}
\begin{lstlisting}
initial begin
  lut[0]=2'd0; lut[1]=2'd0; lut[2]=2'd1; lut[3]=2'd1;
  lut[4]=2'd2; lut[5]=2'd2; lut[6]=2'd1; lut[7]=2'd1;
  lut[8]=2'd3; lut[9]=2'd3; lut[10]=2'd1; lut[11]=2'd1;
  lut[12]=2'd2; lut[13]=2'd2; lut[14]=2'd1; lut[15]=2'd1;
end
\end{lstlisting}
\caption{\texttt{veriflat} evaluates the \texttt{prra\_lut} \texttt{initial}
         block: nested loops and modular arithmetic are replaced by 16 explicit
         constant assignments (4-port arbiter, \texttt{STATE\_OFFSET=0}).}
\label{fig:veriflat-prra}
\end{figure}

The flattened output also benefits simulation: a single-module design with no
hierarchy reduces simulator overhead and can significantly speed up large testbench
runs. Veriparse is available at \url{https://github.com/cclienti/veriparse} under
the LGPLv3 license.

\subsection{License}

HyNoC has been in development since 2013, as reflected in the copyright headers
of every RTL source file. The source code was first published in 2019; the
repository was formally placed under the
\textbf{CERN-OHL-P~v2}~license~\cite{cernohl} in 2026. This permissive open
hardware license allows use, modification, and redistribution with no copyleft
obligation on the end product. The complete source, including RTL, testbenches,
documentation, and build infrastructure, is available at:
\url{https://github.com/cclienti/verilog-ip}.
