\section{Related Work}
\label{sec:related}

NoC architectures span a broad design space, comprehensively covered
in~\cite{dally2004}; this section reviews the dimensions most directly relevant
to HyNoC's design choices.

\subsection{Switching Strategies}

Three main switching strategies are found in the NoC literature.
\emph{Store-and-forward} switching requires a complete packet to be buffered at
each router before forwarding, providing clean error isolation but imposing large
buffer requirements and high latency~\cite{dally2001}.
\emph{Wormhole switching}~\cite{dally1987} pipelines flits across routers,
dramatically reducing buffer depth requirements; latency depends on path length
and contention.
\emph{Circuit switching}~\cite{kumar2002} reserves a dedicated path before
transmission, eliminating mid-network contention at the cost of a setup overhead
proportional to route length before the first data flit is delivered.

Hybrid approaches have been explored. Æthereal~\cite{goossens2005} combines
guaranteed-throughput circuit-switched slots with best-effort wormhole traffic on
the same physical links using time-division multiplexing. HyNoC takes a different
hybrid point: it establishes a dedicated path through a hop-by-hop request/grant
handshake (the circuit phase), then streams payload flits in wormhole fashion
along that reserved path (the data phase). Unlike Æthereal, HyNoC does not
multiplex traffic in time: once a path is open, it is held exclusively for the
duration of the packet, and no other packet can pre-empt it on the same egress
port. The setup latency — one request/grant round per hop — is paid once per
packet and is bounded by the route length, which is acceptable for the long-burst
transfers typical of VLIW inter-core communication.

\subsection{Routing Algorithms}

XY deterministic routing~\cite{dally2001} is simple and deadlock-free on 2D
meshes but provides only a single path between any pair of nodes. Adaptive
routing~\cite{duato1993} improves load balancing but requires more complex router
logic and typically needs virtual channels to avoid deadlock.

\emph{Source routing} encodes the complete route in the packet header at the
sender. This approach, studied for NoCs in~\cite{liwei2007} and~\cite{mubeen2010},
shifts routing complexity from the router to the sending node or to an offline
compilation step. The router itself becomes simpler: it only needs to decode the
next hop from the current flit, forward it, and update the index. Source routing
naturally supports any topology without per-router routing table storage, and
allows the sender to choose among multiple paths. This compile-time route
assignment property is particularly attractive for VLIW many-core systems, where
communication patterns are statically known and can be scheduled to avoid
contention (see Section~\ref{sec:target}).

Source routing has also been adopted in production VLIW many-core NoCs: the
Kalray MPPA2-256 uses a wormhole NoC with feed-forward source routing, where the
complete route is encoded in the header flit and each router forwards based solely
on a local offset extraction~\cite{dinechin2017}. This production deployment
validates the compile-time route assignment model that HyNoC targets.

HyNoC adopts source routing with a compact \emph{relative} hop encoding: since a
packet cannot exit from the same port it entered, a router with $N$ ports offers
only $N-1$ egress choices, encoded in $\lceil\log_2(N-1)\rceil$ bits per hop.
This reduces both header overhead and crossbar complexity simultaneously.

\subsection{Virtual Channels}

Virtual channels (VCs), introduced by Dally~\cite{dally1992}, multiplex several
logical channels over a single physical link, providing additional routing paths
and breaking deadlock cycles. Their main drawback is area: each VC requires a
dedicated buffer, and~\cite{mello2005} shows that router area scales nearly
linearly with VC count. On FPGAs, this overhead is particularly significant
because both the application logic and the communication fabric draw from a shared
pool of Block RAM (BRAM) and distributed LUT RAM resources: adding VCs directly
reduces the memory budget available to the application.

Several works have explored VC reduction or elimination.
Turn-model routing~\cite{glass1992} achieves deadlock freedom without VCs by
restricting the set of turns allowed in the routing graph. HyNoC's
approach---providing path diversity through richer topologies and compile-time
route selection---aligns with this trend, and is analyzed quantitatively in
Section~\ref{sec:switching}.

\subsection{NoC Arbitration}

Arbiter design is a central concern in input-queued routers, where multiple
ingress ports compete for the same egress~\cite{dally2004}.
Matrix arbiters evaluate all (ingress, egress) request pairs in parallel and can
grant in a single cycle regardless of port count, but require $O(N^2)$ state and
combinational logic, making them area-expensive for large routers.
Separable allocators decompose the two-dimensional matching problem into two
independent one-dimensional arbitration steps (one per ingress, one per egress),
reducing area at the cost of potentially requiring multiple rounds to reach a
stable matching~\cite{dally2004}.
Sequential round-robin FSMs scan requests cyclically, introducing up to $N-1$
cycles of latency before granting a pending request.

HyNoC implements a \emph{parallel round-robin arbiter} (PRRA): a set of $N-1$
combinatorial LUT-based state functions that evaluate all pending requests
simultaneously and jump directly to the winning state, regardless of how many
ports are idle. The PRRA matches the single-cycle grant latency of a matrix
arbiter for the common case, while its critical path does not grow with $N$ since
each LUT is evaluated independently. Fairness is maintained through a rotating
priority identical to classical round-robin.

\subsection{FPGA-Targeted NoCs}

FPGA implementations impose constraints not present in ASIC designs: Block RAMs
(BRAMs) are a finite, shared resource, so buffer-heavy NoC designs directly reduce
the memory budget available to the application; clock domain crossing between the
NoC fabric and the attached processing elements must be handled explicitly; and
routing resources constrain achievable clock frequencies~\cite{papamichael2012}.

CONNECT~\cite{papamichael2012} provides a parameterized, synthesizable NoC
generator for FPGAs supporting configurable topologies, VC counts, and buffer
depths, demonstrating that general-purpose FPGA NoCs are feasible. Its
VC-inclusive design trades BRAM for throughput robustness, which is appropriate
when traffic patterns are unpredictable at design time.

Hoplite~\cite{kapre2015} introduced deflection routing on FPGA overlays, achieving
very small area by eliminating input buffers entirely and routing contending flits
onto an alternative output rather than buffering them. HopliteRT~\cite{wasly2017}
extended Hoplite with a real-time traffic class, but deflection fundamentally
introduces non-deterministic, potentially unbounded delivery latency for best-effort
traffic — a property incompatible with the timing constraints of VLIW inter-core
communication.

Xilinx's Versal ACAP~\cite{swarbrick2019} embeds a hardened, fully programmable
NoC in silicon alongside the FPGA fabric, demonstrating that on-chip network
infrastructure has become a first-class concern even in commercial FPGA products.
Its hardened implementation achieves high bandwidth with low latency, but is
vendor-specific and not accessible as a soft IP.

Hermes~\cite{moraes2004}, the direct ancestor of HyNoC, demonstrated low-area
wormhole switching on FPGA with a 2D mesh topology and XY routing. Its
asynchronous variant Hermes-A~\cite{pontes2011} explored per-port independent
clock domains through asynchronous handshaking. HyNoC addresses the same
requirement using synchronous dual-clock FIFOs, which bridge arbitrary clock
domain boundaries at each ingress port without requiring asynchronous logic.

HyNoC targets a distinct point in this space: topology-agnostic source routing
with bounded latency, no virtual channels, and LUT-RAM-based FIFOs that avoid
BRAM consumption, suited to predictable VLIW workloads.

\subsection{VLIW Many-Core Systems}

VLIW processors expose multiple functional units to the compiler, which schedules
operations explicitly in long instruction words~\cite{ellis1986}. This design
philosophy transfers control complexity from hardware to software, producing
simple, area-efficient cores well suited for replication. Signal processing,
neural network inference, and scientific computing are representative workloads.

Distributed VLIW many-core systems---exemplified by the Kalray
MPPA~\cite{dinechin2013}---replicate VLIW cores connected through a dedicated
NoC, with subsequent generations~\cite{dinechin2017} adopting source routing
to preserve deterministic latency guarantees across the fabric. In such systems, the communication graph is known at compile time: the
compiler can assign source routes, schedule packet injections to avoid egress port
collisions, and guarantee bounded communication latency on the critical path. This
compile-time visibility makes HyNoC's hybrid model particularly effective, as the
bounded circuit-establishment latency (one PRRA grant per hop) feeds directly into
the timing model used by the compiler to schedule inter-core transfers.

\subsection{Positioning}

Table~\ref{tab:positioning} summarizes how HyNoC relates to the principal design
axes discussed above.

\begin{table}[h]
\centering
\footnotesize
\caption{Positioning of representative NoCs}
\label{tab:positioning}
\resizebox{\columnwidth}{!}{%
\begin{tabular}{@{}lllll@{}}
\toprule
Design       & Switching  & Routing    & VCs & Target \\
\midrule
Hermes~\cite{moraes2004}      & Wormhole        & XY (dest.)    & No  & ASIC/FPGA \\
Æthereal~\cite{goossens2005}  & TDM + Wormhole  & Table         & Yes & ASIC \\
CONNECT~\cite{papamichael2012}& Wormhole        & Configurable  & Yes & FPGA \\
HopliteRT~\cite{wasly2017}     & Deflection      & XY (dest.)    & No  & FPGA \\
HyNoC                         & Circuit+Wormhole& Source (rel.) & No  & FPGA \\
\bottomrule
\end{tabular}%
}
\end{table}
